---
title: "facilitation:introduction"
author: "M. Salles"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The package `facilitation` was created to simulate the population dynamics of plant species that
receive facilitation from other species on the early stages of development. The package evolved to allow simulations with a larger
number of species, and varied types of interactions. Currently, it allows for any number of species,
each with any number of life stages, where each stage has it's own death rate, growth rate (except
for the last stage of each species, of course), reproduction rates, and interaction radius,
and where each stage can affect each other stage affecting death, growth or reproduction
rates positively or negatively, with any value.

In addition to the simulation proper, this package includes functions for extracting and
plotting relevant information from the simulation results, as well as a few basic functions
to produce matrix population models that can be compared with the simplest simulations.

The main function in this package is `community`, the function used to run the simulations.
The simulation was implemented in c++ using the package Rcpp, and is acessible from R only through this one function. 

## Running simulations

# Example 1 - the simplest example

The simplest simulation you can run would be of a single population with only one stage.
Still, the individuals of this populations should be able to die, and to reproduce. 

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
